### 2018-03-12 Writing/Thesis/content/abstract.tex
integrate comments part three

As the demand for machine learning functionality increases dramatically, automated machine learning (AutoML) aims to (partially) automate the creation of machine learning applications. Current AutoML approaches, however, often search for a fitting learning algorithm for a new data set without explicitly considering how properties of the data set might influence algorithm performances. Furthermore, in comparison to recommending a ranking of learning algorithms, this has the disadvantage that no alternatives are presented. Due to a certain inaccuracy of the prediction, these may have an equal or even better performance than the first suggestion regarding the examined data set.

@@

Da die Nachfrage nach Funktionalität im Bereich des maschinellen Lernens dramatisch ansteigt, hat automatisiertes maschinelles Lernen (AutoML) das Ziel, die Erstellung von Anwendungen im Kontext des maschinellen Lernens (teilweise) zu automatisieren. Aktuelle Ansätze dieser Art suchen jedoch oft nach einem Lernalgorithmus für einen neuen Datensatz, ohne explizit zu berücksichtigen, wie Eigenschaften des Datensatzes die Performanz der Algorithmen beeinflussen können. Außerdem hat dies im Vergleich zu dem Vorschlag eines Rankings von Lernalgorithmen den Nachteil, dass keine Alternativen präsentiert werden. Diese können allerdings, aufgrund der Ungenauigkeit der Vorhersagen, gleichwertig oder sogar bessere Genauigkeiten auf diesem Datensatz haben.

>>>>

As the demand for machine learning functionality increases dramatically, automated machine learning (AutoML) aims to (partially) automate the creation of machine learning applications. Current AutoML approaches, however, often search for a single fitting learning algorithm for a new data set without explicitly considering how properties of the data set influence algorithm performances. Furthermore, in comparison to recommending a ranking of learning algorithms, this has the disadvantage that no alternatives are presented. Due to a certain inaccuracy of the prediction, these may have an equal or even better performance than the first suggestion regarding the examined data set.

@@

Da die Nachfrage nach Funktionalität im Bereich des maschinellen Lernens dramatisch ansteigt, hat automatisiertes maschinelles Lernen (AutoML) das Ziel, die Erstellung von Anwendungen im Kontext des maschinellen Lernens (teilweise) zu automatisieren. Aktuelle Ansätze dieser Art suchen jedoch oft nach einem Lern-algorithmus für einen neuen Datensatz, ohne explizit zu berücksichtigen, wie Eigenschaften des Datensatzes die Performanz der Algorithmen beeinflussen können. Außerdem hat dies im Vergleich zu dem Vorschlag eines Rankings von Lernalgorithmen den Nachteil, dass keine Alternativen präsentiert werden. Diese können allerdings, aufgrund der Ungenauigkeit der Vorhersagen, gleichwertig oder sogar bessere Genauigkeiten auf diesem Datensatz haben.

### 2018-03-12 Writing/Thesis/content/chapter-approach.tex
integrate comments part three

In general, the aim is to predict a ranking of algorithms based on properties, or meta features of a data set. This means, that as training data for a ranking approach (ranker), a number of performance values of classifiers need to be recorded on data sets in a first pre-processing phase, for which also meta features are to be computed. The table of this collected data is illustrated in Table \ref{tab:performanceValues}, for n meta features, k classifiers and m data sets. This approach to ranking is realized here, as pointed out before, in a regression based and preference based approach, which are explained in detail in the following sections.

\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X | X | X | X | X | X | X}
		%\hline
		MF 1			& MF 2		& ... 	& MF n		& PV 1 		& PV 2 		&	...	&	PV k 		\\ \hline
		$v_{11}$		& $v_{12}$	& ...	& $v_{1n}$	& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ 
		$v_{21}$		& $v_{22}$	& ...	& $v_{2n}$	& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\ 
		...			& ...		& ...	& ...		& ...		& ...		&	...	&	...			\\ 
		$v_{m1}$		& $v_{m2}$	& ... 	& $v_{mn}$	& $p_{2n}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
	\end{tabularx}
	\caption{Training data for the rankers.}
	\label{tab:performanceValues}
\end{table}

\subsection{Regression Based Ranking}
% How is the regression ranking done
One possibility to derive a ranking of classifiers from this information when given a new data set is to use regression models. The idea is to use separate regression models to predict a performance value for each classifier, and to subsequently derive an ordering from these predictions. This is done by splitting the data set compiled beforehand (see Tab. \ref{tab:performanceValues}) into separate data sets that each contain all meta features for all data sets, but only the performance values of one classifier, as illustrated in Table \ref{tab:regressionTables}. The target feature on these individual data sets, the performance value of the classifier, is a numeric value, and thus, a regression model can be trained on each of them. All regression models therefore try to learn the target function \textit{meta features}$\rightarrow$\textit{performance value} for their respective classifier. Hence, for a query instance, a new data set, after computing the meta features, these are fed into each regression model and the predicted performance value for each classifier is saved. In a second step, the classifiers are ordered according to the predictions. This generation of a ranking is presented in Figure \ref{fig:regression_ranker_model}.

\begin{table}[h]
\centering
\resizebox{\textwidth}{!}{%
	\begin{tabularx}{1.1\textwidth}{X | X | X | X}
		%\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 1	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{11}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{21}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m1}$				\\ \hline\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 2 	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{12}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{22}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m2}$					 
	\end{tabularx}
}	
\vspace{1em}
...
\vspace{1em}	
\resizebox{\textwidth}{!}{%
	\begin{tabularx}{1.1\textwidth}{X | X | X | X}
		%\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value k 	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{1k}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{2k}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{mk}$					 
	\end{tabularx}
}
	\caption{How the regression ranker processes the training data. Performance data for each classifier are in a separate table, which are then used to train separate regression models.}
	\label{tab:regressionTables}
\end{table}

\begin{figure}
\centering
\includegraphics[scale=1]{gfx/regression_models.pdf}
\caption{An overview of how a regression based ranker constructs a ranking.}
\label{fig:regression_ranker_model}
\end{figure}

\subsection{Preference Based Ranking}
% How is the preference ranking done
The second possibility considered in this context is using preference learning to predict a ranking. Each instance of the data set generated beforehand (see Tab. \ref{tab:performanceValues}) contains meta feature information for the considered data set and performance values of all classifiers. Similar to the regression alternative, the performance values can be converted to preference information by sorting the corresponding classifiers by their performance values for each data set. This leads to an ordering of classifiers associated with each instance, and implies that the preference learning task at hand is label ranking. In this case, there exists only one label ranking model which is fed the computed meta data for a new data set and returns an ordering of classifiers, which is depicted in Figure \ref{fig:preference_ranker_model}. Thereby, it attempts to learn the mapping from meta features to an ordering of classifiers directly.

@@

\begin{figure}
\centering
\includegraphics[scale=1]{gfx/label_ranking_model.pdf}
\caption{An overview of how a preference based ranker constructs a ranking.}
\label{fig:preference_ranker_model}
\end{figure}

\section{Implementation}
In general, all implementations for the approach are carried out in Java, particularly Java 8. However, some additional packages were used, which are pointed out briefly. For the implementation of the regression models, WEKA was used, a popular libary of machine learning algorithms that includes algorithms for classification, regression, and provides help in the evaluation of these learning algorithms \cite{hall2009weka}. Regarding the preference algorithms, the jPL framework was used \cite{intelligent2017jpl}. The jPL framework is a Java framework for the evaluation of preference learning algorithms, it implements several tasks from the context of preference learning, including label ranking, and also provides a representation for data sets that contain label ranking information. The list of meta features used is taken from OpenML \cite{OpenML2013}, a website that not only provides a large number of openly accessible data sets, but also records performance values of learning algorithms on these data sets, and features properties of data sets. Thus the meta features were calculated with the help of an implementation provided by OpenML in its Evaluation Engine \cite{openMLEvaluationEngine}; The full list of meta features is included in Table \ref{tab:metaFeatureDetails} in the Appendix.

>>>>

In general, the aim is to predict a ranking of algorithms based on properties, or meta features of a data set. This means, that as training data for a ranking approach (ranker), a number of performance values of classifiers need to be recorded on data sets in a first pre-processing phase, for which also meta features are to be computed. The table of this collected data is illustrated in Table \ref{tab:performanceValues}, for n meta features, k classifiers and m data sets. This approach to ranking is realized here, as pointed out before, in a regression-based and preference-based approach, which are explained in detail in the following sections.

\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X | X | X | X | X | X | X}
		%\hline
		MF 1			& MF 2		& ... 	& MF n		& PV 1 		& PV 2 		&	...	&	PV k 		\\ \hline
		$v_{11}$		& $v_{12}$	& ...	& $v_{1n}$	& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ 
		$v_{21}$		& $v_{22}$	& ...	& $v_{2n}$	& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\ 
		...			& ...		& ...	& ...		& ...		& ...		&	...	&	...			\\ 
		$v_{m1}$		& $v_{m2}$	& ... 	& $v_{mn}$	& $p_{m1}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
	\end{tabularx}
	\caption{Training data for the rankers.}
	\label{tab:performanceValues}
\end{table}

\subsection{Regression-Based Ranking}
% How is the regression ranking done
One possibility to derive a ranking of classifiers from this information when given a new data set is to use regression models. The idea is to use separate regression models to predict a performance value for each classifier, and to subsequently derive an ordering from these predictions. This is done by splitting the data set compiled beforehand (see Tab. \ref{tab:performanceValues}) into separate data sets that each contain all meta features for all data sets, but only the performance values of one classifier, as illustrated in Table \ref{tab:regressionTables}. The target feature on these individual data sets, the performance value of the classifier, is a numeric value, and thus, a regression model can be trained on each of them. All regression models therefore try to learn the target function \textit{meta features}$\rightarrow$\textit{performance value} for their respective classifier. Hence, for a query instance, here represented by a new data set, the first step is to compute the meta features. Afterwards, these are fed into each regression model and the predicted performance value for each classifier is saved. In a second step, the classifiers are ordered according to the predictions. This generation of a ranking is presented in Figure \ref{fig:regression_ranker_model}.

\begin{table}[h]
\centering
\resizebox{\textwidth}{!}{%
	\begin{tabularx}{1.1\textwidth}{X | X | X | X}
		%\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 1	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{11}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{21}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m1}$				\\ \hline\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 2 	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{12}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{22}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m2}$					 
	\end{tabularx}
}	
\vspace{1em}
$\vdots$
\vspace{1em}	
\resizebox{\textwidth}{!}{%
	\begin{tabularx}{1.1\textwidth}{X | X | X | X}
		%\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value k 	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{1k}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{2k}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{mk}$					 
	\end{tabularx}
}
	\caption{How the regression ranker processes the training data. Performance data for each classifier are in a separate table, which are then used to train separate regression models.}
	\label{tab:regressionTables}
\end{table}

\begin{figure}
\centering
\includegraphics[scale=1]{gfx/regression_models.pdf}
\caption{An overview of how a regression-based ranker constructs a ranking.}
\label{fig:regression_ranker_model}
\end{figure}

\subsection{Preference-Based Ranking}
% How is the preference ranking done
The second possibility considered in this context is using preference learning to predict a ranking. Each instance of the data set generated beforehand (see Tab. \ref{tab:performanceValues}) contains meta feature information for the considered data set and performance values of all classifiers. Similar to the regression alternative, the performance values can be converted to preference information by sorting the corresponding classifiers by their performance values for each data set. This leads to an ordering of classifiers associated with each instance, and implies that the preference learning task at hand is label ranking. In this case, there exists only one label ranking model which is fed the computed meta data for a new data set and returns an ordering of classifiers, which is depicted in Figure \ref{fig:preference_ranker_model}. Thereby, it attempts to learn the mapping from meta features to an ordering of classifiers directly.

@@

\begin{figure}
\centering
\includegraphics[scale=1]{gfx/label_ranking_model.pdf}
\caption{An overview of how a preference-based ranker constructs a ranking.}
\label{fig:preference_ranker_model}
\end{figure}

\section{Implementation}
In general, all implementations for the approach are carried out in Java, particularly Java 8. However, some additional packages were used, which are pointed out briefly. For the implementation of the regression models, WEKA was used, a popular libary of machine learning algorithms that includes algorithms for classification, regression, and provides help in the evaluation of these learning algorithms \cite{hall2009weka}. Regarding the preference algorithms, the jPL framework was used \cite{intelligent2017jpl}. The jPL framework is a Java framework for the evaluation of preference learning algorithms, it implements several tasks from the context of preference learning, including label ranking, and also provides a representation for data sets that contain label ranking information. The list of meta features used is taken from OpenML \cite{OpenML2013}, a website that not only provides a large number of openly accessible data sets, but also records performance values of learning algorithms on these data sets, and features properties of data sets. Thus the meta features were calculated with the help of an implementation provided by OpenML in its Evaluation Engine \cite{openMLEvaluationEngine}; the full list of meta features is included in Table \ref{tab:metaFeatureDetails} in the Appendix.

### 2018-03-12 Writing/Thesis/content/chapter-conclusion.tex
integrate comments part three

% Recommendations for future work
\section{Future Work}
\label{sec:conclusion:future}
% More evaluation - meta features
As the results have shown that the approach taken in this thesis has worked out reasonably well, for example when considering the regression-based approach using random forest, many possibilities for additional work arise. An intuitive thought would be to extend the evaluation of the tool, for instance in terms of meta features. Additional sets of meta features could be evaluated, like adding implementations for additional meta features, or considering using only light probing by incorporating the performance values for usually cheap algorithms in the meta features. Since the significant advantage of any approach was lost regarding best three loss when moving from the full meta data to the reduced meta data without probing, this might be especially interesting. One could consider adding the meta feature groups for DecisionStump, RandomTreeDepth2, REPTreeDepth2, and J48.0001, which would add approximately 12 milliseconds to the already existing 3 milliseconds of calculation time for the meta features in the mean, which seemss reasonable. An effect on the time and quality of predictions for larger data sets would have to be examined still.

% More evaluation - loss - time & compare agains Jan van Rijn
Furthermore, more insights could be gained about whether this approach is competitive by comparing it with other ranking approaches, for example like the one proposed by \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} \cite{DBLP:journals/ml/AbdulrahmanBRV18}. In this regard it would also be interesting to implement the loss and time-loss curves proposed by the authors, which show how loss decreases as one advances in the predicted ranking and tries out the recommended algorithms, and at what cost in the sense of time the sampling of algorithms comes respectively.

>>>>

% Recommendations for future work
\section{Future Work}
\label{sec:conclusion:future}
% More evaluation - meta features
As the results have shown that the approach taken in this thesis has worked out reasonably well, for example when considering the regression-based approach using random forest, many possibilities for additional work arise. An intuitive thought would be to extend the evaluation of the tool, for instance in terms of meta features. Additional sets of meta features could be evaluated, like adding implementations for additional meta features, or considering using only light probing by incorporating the performance values for usually cheap algorithms in the meta features. Since the significant advantage of any approach was lost regarding best three loss when moving from the full meta data to the reduced meta data without probing, this might be especially interesting. One could consider adding the meta feature groups for DecisionStump, RandomTreeDepth2, REPTreeDepth2, and J48.0001, which would add approximately 12 milliseconds to the already existing 3 milliseconds of calculation time for the meta features in the mean, which seems reasonable. An effect on the time and quality of predictions for larger data sets would have to be examined still.

% More evaluation - loss - time & compare agains Jan van Rijn
Furthermore, more insights could be gained about whether this approach is competitive by comparing it with other ranking approaches, for example with the one proposed by \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} \cite{DBLP:journals/ml/AbdulrahmanBRV18}. In this regard it would also be interesting to implement the loss and time-loss curves proposed by the authors, which show how loss decreases as one advances in the predicted ranking and tries out the recommended algorithms, and at what cost in the sense of time the sampling of algorithms comes respectively.

### 2018-03-12 Writing/Thesis/content/chapter-evaluation.tex
integrate comments part three

% Evaluation Measures used & computed
As rankings returned by this oracle represent the ideal solution, the predicted rankings are compared with them through the measures presented in chapter \ref{sec:fundamentals}. These include the Kendall rank correlation coefficient, performance loss and best three loss regarding classifier performance. For all three measures, it is computed whether any difference in performance is significant, by means of the p-value for the Mann-Whitney U. The regression based rankers pose a special case: internally, they predict a performance value for each classifier, which therefore can be compared to the actual performance values to show how well they are predicted. This is done by computing the root mean square error between the predicted and actual performance values. In summary, it is desirable for the rankers to come as close as possible to the correct ranking, which is reflected by a high rank correlation and a low loss and root mean square error.

% Baseline
Furthermore, we are interested in the question as to what degree knowing about the properties of a data set influences the quality of rankings. Therefore, a ranker that is agnostic to the meta features of a query data set, that is that will always return the same ranking for any data set, is used as a baseline. More specifically, a best algorithm strategy that iteratively determines a ranking by counting the number of data sets where an algorithm is the best choice, is implemented. That means the first algorithm in the best algorithm ranking is the classifier that performs best on most data sets, the second is the best on most data sets when only rankings excluding the first algorithm are considered, and so forth. This baseline is evaluated in the same way as the preference rankers; as it does not predict performance values, the root mean square error of predicted performance values cannot be computed. Ideally, rankings returned by the preference and regression based rankers should then be statistically significantly better than the static baseline, as this would indicate a connection of certain meta features and a performance-induced ranking of classifiers for a data set.

\section{Experimental Setup}
In the following paragraphs, it is briefly summarized under which conditions the experiments which led to the results discussed in the next section were observed. This includes which classifiers and data sets were chosen, and what the specifications of the machines the evaluation was executed on were. It is described how the evaluation was carried out, and which specific regression-based and preference-based implementations were used.

@@

% Which data sets
Data sets for the analysis were gathered from OpenML. From all data sets considered as 'active' on OpenML, which yields 2050 data sets that have been approved with no severe issues found for them so far \cite{openMLGuide}, all data sets that comply with the constraints of the learning problem at hand were selected. Only data sets in the .ARFF format with a defined, nominal target feature which were not specifically designed for streaming analysis\footnotemark{} were considered, which resulted in a reduced selection of 812 instances. Since this amount of data sets hindered the evaluation considerably, large data sets with more than 1000 instances or 100 features were removed as well, leading to a final selection of 448 data sets. Even though evaluation was only carried out on the shorter list, both the list of 812 and 448 data sets are included in the supplementary material for completeness.

\footnotetext{Data sets that contained the substring 'BNG' in their name for Bayesian Network Generator, which contain data artificially generated by a Bayesian Network \cite{van2014algorithm} for the sake of data stream analysis were not included in the evaluation.}

% How base performance data generated
The performance data of the classifiers for the selected data sets was generated on a linux cluster with nodes consisting of two Intel(R) Xeon(R) E5-2670 processors running at 2.6GHz, 64GB RAM. For the computation of a single performance value of a classifier on a data set, two CPU cores and 16GB RAM were used, with a timeout of eight hours. Up to 150 of such processes were executed in parallel. For each of the classifiers, the predictive accuracy (the percentage of correctly classified instances in the data set) was recorded on each data set by means of five times stratified Monte-Carlo cross validation with a 70/30 split in training and test data. The stratified split was generated with the help of JAICore, \textquotesingle A Java library for infrastructural classes and basic algorithms in the area reasoning, search, and machine learning\textquotesingle [Reference Missing]. When a timeout occurred or the evaluation failed otherwise, the predictive accuracy was set to zero.

@@

% How find best version of preference and regression ranker
Furthermore, four alternatives were selected for a regression based and preference based alternative each, to get a general idea of how well the respective approach might be suited for the problem. For the regression based approach, the algorithms chosen were random forest, REPTree, M5P, and linear regression. For all of them, the WEKA implemenation \cite{hall2009weka} was used, and the algorithms where used with the standard hyperparameters set by WEKA. As the preference-based ranking falls under the category of label ranking, and in the jPL-framework, which was used for the implementation of the label ranking algorithms and data set representations, only two alternatives for label ranking are implemented \cite{intelligent2017jpl}, the other two alternatives were generated by modifying the hyperparameters. The implemented alternatives are label ranking by pairwise comparison and instance-based label ranking. As in early tests it became apparent that the instance-based approach might hold more potential, for label ranking by pairwise comparison, only the default configuration dictated by jPL was used. For instance-based label ranking, three different configurations were evaluated, the default configurations and two custom ones. For the first customization, the rank aggregation algorithm used by the label ranker was set to Kemeny-Young. For the second customization, additionally, the number of neighbors of the base learner of the label ranker, namely k nearest neighbor (kNN), was set to the square root of the number of instances in the training data set. All of the described rankers are included in an overview in Table \ref{tab:methods}. In the following section, these eight variants are compared with the baseline and oracle mentioned in the previous section, and among each others.

@@

In the following subsections, results of the evaluation are discussed in detail. First, the quality of the predictions of the rankers is examined. Then, the times required for building the rankers and for predictions made as well as for the calculation of the meta features is reviewed. Last, additional insights gathered during the evaluation are pointed out.

@@

Summarizing the observed results, in general, a regression based approach shows an indication to be stronger than a preference based approach. Specifically, using random forest as a regression model is the best solution observed in the evaluation, and label ranking by pairwise comparison the weakest, as it falls behind the other ranking approaches and the baseline often. A surprising result is that the label ranking approaches achieve very similar results with or without probing.

>>>>

% Evaluation Measures used & computed
As rankings returned by this oracle represent the ideal solution, the predicted rankings are compared with them through the measures presented in chapter \ref{sec:fundamentals}. These include the Kendall rank correlation coefficient, performance loss and best three loss regarding classifier performance. For all three measures, it is computed whether any difference in performance is significant, by means of the p-value for the Mann-Whitney U. The regression-based rankers pose a special case: internally, they predict a performance value for each classifier, which therefore can be compared to the actual performance values to show how well they are predicted. This is done by computing the root mean square error between the predicted and actual performance values. In summary, it is desirable for the rankers to come as close as possible to the correct ranking, which is reflected by a high rank correlation and a low loss and root mean square error.

% Baseline
Furthermore, we are interested in the question as to what degree knowing about the properties of a data set influences the quality of rankings. Therefore, a ranker that is agnostic to the meta features of a query data set, meaning that it will always return the same ranking for any data set, is used as a baseline. More specifically, a best algorithm strategy that iteratively determines a ranking by counting the number of data sets where an algorithm is the best choice, is implemented. That means the first algorithm in the best algorithm ranking is the classifier that performs best on most data sets, the second is the best on most data sets when only rankings excluding the first algorithm are considered, and so forth. This baseline is evaluated in the same way as the preference rankers; as it does not predict performance values, the root mean square error of predicted performance values cannot be computed. Ideally, rankings returned by the preference and regression based rankers should then be statistically significantly better than the static baseline, as this would indicate a connection of certain meta features and a performance-induced ranking of classifiers for a data set.

\section{Experimental Setup}
In the following paragraphs, it is briefly summarized under which conditions the experiments which led to the results discussed in the next section were observed. This includes which classifiers and data sets were chosen, and the specifications of the machines the evaluation was executed on. It is described how the evaluation was carried out, and which specific regression-based and preference-based implementations were used.

@@

% Which data sets
Data sets for the analysis were gathered from OpenML. From all data sets considered as `active' on OpenML, which yields 2050 data sets that have been approved with no severe issues found for them so far \cite{openMLGuide}, all data sets that comply with the constraints of the learning problem at hand were selected. Only data sets in the .ARFF format with a defined, nominal target feature which were not specifically designed for streaming analysis\footnotemark{} were considered, which resulted in a reduced selection of 812 instances. Since this amount of data sets hindered the evaluation considerably, large data sets with more than 1000 instances or 100 features were removed as well, leading to a final selection of 448 data sets. Even though evaluation was only carried out on the shorter list, both the list of 812 and 448 data sets are included in the supplementary material for completeness.

\footnotetext{Data sets that contained the substring `BNG' in their name for Bayesian Network Generator, which contain data artificially generated by a Bayesian Network \cite{van2014algorithm} for the sake of data stream analysis were not included in the evaluation.}

% How base performance data generated
The performance data of the classifiers for the selected data sets was generated on a linux cluster with nodes consisting of two Intel(R) Xeon(R) E5-2670 processors running at 2.6GHz, 64GB RAM. For the computation of a single performance value of a classifier on a data set, two CPU cores and 16GB RAM were used, with a timeout of eight hours. Up to 150 of such processes were executed in parallel. For each of the classifiers, the predictive accuracy (the percentage of correctly classified instances in the data set) was recorded on each data set by means of five times stratified Monte-Carlo cross validation with a 70/30 split in training and test data. The stratified split was generated with the help of JAICore, `A Java library for infrastructural classes and basic algorithms in the area reasoning, search, and machine learning' [Reference Missing]. When a timeout occurred or the evaluation failed otherwise, the predictive accuracy was set to zero.

@@

% How find best version of preference and regression ranker
Furthermore, four alternatives were selected for a regression-based and preference-based alternative each, to get a general idea of how well the respective approach might be suited for the problem. For the regression-based approach, the algorithms chosen were random forest, REPTree, M5P, and linear regression. For all of them, the WEKA implemenation \cite{hall2009weka} was used, and the algorithms where used with the standard hyperparameters set by WEKA. As the preference-based ranking falls under the category of label ranking, and in the jPL-framework, which was used for the implementation of the label ranking algorithms and data set representations, only two alternatives for label ranking are implemented \cite{intelligent2017jpl}, the other two alternatives were generated by modifying the hyperparameters. The implemented alternatives are label ranking by pairwise comparison and instance-based label ranking. As in early tests it became apparent that the instance-based approach might hold more potential, for label ranking by pairwise comparison, only the default configuration dictated by jPL was used. For instance-based label ranking, three different configurations were evaluated, the default configurations and two custom ones. For the first customization, the rank aggregation algorithm used by the label ranker was set to Kemeny-Young. For the second customization, additionally, the number of neighbors of the base learner of the label ranker, namely k nearest neighbor (kNN), was set to the square root of the number of instances in the training data set. All of the described rankers are included in an overview in Table \ref{tab:methods}. In the following section, these eight variants are compared with the baseline and oracle mentioned in the previous section, and among each others.

@@

In the following subsections, results of the evaluation are discussed in detail. First, the quality of the predictions of the rankers is examined. Then, the times required for building the rankers and for predictions made as well as for the calculation of the meta features is reviewed. At last, additional insights gathered during the evaluation are pointed out.

@@

Summarizing the observed results, in general, a regression-based approach shows an indication to be stronger than a preference-based approach. Specifically, using random forest as a regression model is the best solution observed in the evaluation, and label ranking by pairwise comparison the weakest, as it falls behind the other ranking approaches and the baseline often. A surprising result is that the label ranking approaches achieve very similar results with or without probing.
